A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-17 paper/paper.Rnw
force a specific model version

newest_model <- get_newest(dir = model_path, pattern = "weights.h5")
newest_data_file <- file.path(modeldir, "RProcessedImages",
                              newest_model$process_dir, "cropped_photos.Rdata")

>>>>

# newest_model <- get_newest(dir = model_path, pattern = "weights.h5")
newest_model <- list(path = file.path(model_path, "20190514-155453"),
    base_file = "2019-05-14_19:45:22_vgg16_onehotaug_9class_256-weights.h5",
    prefix = "vgg16_onehotaug_9class_256", start_date = "2019-05-14_19:45:22",
    process_dir = "20190514-155453")
newest_data_file <- file.path(modeldir, "RProcessedImages",
                              newest_model$process_dir, "cropped_photos.Rdata")
